Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-06-09 doc/manuscript/ESSDmanuscript.Rmd
revise language on gains & losses
#48

To improve data accessibility for preparing greenhouse gas estimates, the IPCC created the Emission Factor Database (EFDB; [https://www.ipcc-nggip.iges.or.jp/EFDB/main.php](https://www.ipcc-nggip.iges.or.jp/EFDB/main.php)), which is intended as a recognized library of emission factors and other parameters that can be used for estimating greenhouse gas emissions and removals.
The EFDB can be used both for efforts to tally a nation's intended or accomplished greenhouse gas reductions, or as a basis of comparison for external parties to evaluate these inventories. 
The EFDB encourages researchers to submit estimates of emission factors or other related parameters from peer-reviewed journal papers or other accepted sources for inclusion in the database. 
In the case of forests, emission factors include C stocks, net increments ("stock changes"), and fluxes ("gains" and "losses") for various pools [@ipcc_2006_2006;@ipcc_2019_2019].

@@

With input from the IPCC's Technical Support Unit, we reviewed the list of ForC variables to identify those that were relevant to EFDB and to appropriately map them into EFDB (Fig. `r fig_variable_mapping`).
For each C pool (Table `r table_pools`), we identified variables representing organic matter or C stocks, stock changes (a.k.a. "net annual increments" by IPCC, "increments" in ForC), gains (a.k.a. "gross annual increments" by IPCC, "fluxes" in ForC), and losses ("fluxes" in ForC).
As described in section `r section_new_variables`, we also defined `r n_new_variables` new EFDB-relevant variables that were not previously represented in ForC. 
It is important to note that the correspondence of ForC variables to IPCC criteria often depends upon measurement protocols ("important sources of estimate variation" in Table `r table_pools`).
For example, ForC records of biomass and dead wood vary in the minimum stem diameter censused, such that some records would match the IPCC criteria whereas others would not.
Information on minimum diameters censused and other important sources of methodological variation are recorded as covariates in ForC and mapped into the EFDB field *Other Properties* (`r table_ForCfieldmapping`).
Details on the mapping of ForC variables to EFDB -- including associated covariates, IPCC pools (Table `r table_pools`) and relevant equations [@ipcc_2006_2006] -- are documented in the file ForC_variables_mapping.csv in the GitHub repository associated with this publication IPCC-EFDB-integration repository in ForC-db organization ([https://github.com/forc-db/IPCC-EFDB-integration](https://github.com/forc-db/IPCC-EFDB-integration)).

>>>>

To improve data accessibility for preparing greenhouse gas estimates, the IPCC created the Emission Factor Database (EFDB; [https://www.ipcc-nggip.iges.or.jp/EFDB/main.php](https://www.ipcc-nggip.iges.or.jp/EFDB/main.php)), which is intended as a recognized library of emission factors and other parameters that can be used for estimating greenhouse gas emissions and removals.
The EFDB can be used both for efforts to tally a nation's intended or accomplished greenhouse gas reductions, or as a basis of comparison for external parties to evaluate these inventories. 
The EFDB encourages researchers to submit estimates of emission factors or other related parameters from peer-reviewed journal papers or other accepted sources for inclusion in the database. 
In the case of forests, emission factors include C stocks, net annual increments, and annual fluxes for various pools [@ipcc_2006_2006;@ipcc_2019_2019].

@@

With input from the IPCC's Technical Support Unit, we reviewed the list of ForC variables to identify those that were relevant to EFDB and to appropriately map them into EFDB (Fig. `r fig_variable_mapping`).
For each C pool (Table `r table_pools`), we identified variables representing organic matter or C stocks, net annual increments, influxes (a.k.a. "gross annual increments" by IPCC), and outfluxes.
As described in section `r section_new_variables`, we also defined `r n_new_variables` new EFDB-relevant variables that were not previously represented in ForC. 
It is important to note that the correspondence of ForC variables to IPCC criteria often depends upon measurement protocols ("important sources of estimate variation" in Table `r table_pools`).
For example, ForC records of biomass and dead wood vary in the minimum stem diameter censused, such that some records would match the IPCC criteria whereas others would not.
Information on minimum diameters censused and other important sources of methodological variation are recorded as covariates in ForC and mapped into the EFDB field *Other Properties* (`r table_ForCfieldmapping`).
Details on the mapping of ForC variables to EFDB -- including associated covariates, IPCC pools (Table `r table_pools`) and relevant equations [@ipcc_2006_2006] -- are documented in the file ForC_variables_mapping.csv in the GitHub repository associated with this publication IPCC-EFDB-integration repository in ForC-db organization ([https://github.com/forc-db/IPCC-EFDB-integration](https://github.com/forc-db/IPCC-EFDB-integration)).

### 2023-06-09 doc/manuscript/ESSDmanuscript.tex
revise language on gains & losses
#48

\textbf{Abstract.} Forests are critical for climate change mitigation
and constitute a substantial portion of planned net emissions reductions
under the 2015 Paris Agreement. However, the efficacy of greenhouse gas
mitigation planning and reporting is dependent upon the quality of
available emission factors data, including forest carbon (C) stocks and
changes therein. Tens of thousands of relevant forest C estimates have
been published, yet are not readily accessible to the practitioners
compiling national greenhouse gas inventories. Many of these data have,
however, been compiled in the Global Forest C database (ForC;
https://forc-db.github.io/) and stand to be of value to greenhouse gas
inventories if made available through the Emission Factor Database
(EFDB) of the International Panel on Climate Change (IPCC). Here, we
develop and document a process for semi-automated submission of data
from ForC into the EFDB, assess the data available and submitted to
date, and provide recommendations for improving forest data collection,
analysis, and reporting to improve inventories of forest-sector
greenhouse gas emissions and removals. We begin by reconciling
terminology and mapping ForC fields into EFDB. This process required
some updates to the ForC database structure, leading to the release of a
new version of ForC (v4.0; described here). As of June 08, 2023, ForC
contained \textasciitilde19316 independent records relevant to EFDB,
1438 of which have been submitted to date. Among the data in ForC, there
is disproportionate representation of biomass (particularly aboveground)
stocks, with far fewer records for dead organic matter and soil C, and
relatively few or no records for net annual increments or C fluxes into
(gains) or out of (losses) the IPCC-defined C pools. Geographic
representation is also quite uneven, with the highest densities of
relevant records in temperate forests, and with relatively scant
representation of tropical forests in Africa and Asia. In the future,
forest C estimates in EFDB can be improved through targeted research to
fill critical gaps, reporting of information required by IPCC, and
continued submission of data from scientific publications to the EFDB.
Given that climate change is rapidly impacting the world's forests,
timely reporting of recent estimates will be especially critical to
accurate forest C inventories.

@@

To improve data accessibility for preparing greenhouse gas estimates,
the IPCC created the Emission Factor Database (EFDB;
\url{https://www.ipcc-nggip.iges.or.jp/EFDB/main.php}), which is
intended as a recognized library of emission factors and other
parameters that can be used for estimating greenhouse gas emissions and
removals. The EFDB can be used both for efforts to tally a nation's
intended or accomplished greenhouse gas reductions, or as a basis of
comparison for external parties to evaluate these inventories. The EFDB
encourages researchers to submit estimates of emission factors or other
related parameters from peer-reviewed journal papers or other accepted
sources for inclusion in the database. In the case of forests, emission
factors include C stocks, net increments (``stock changes''), and fluxes
(``gains'' and ``losses'') for various pools
\citep{ipcc_2006_2006, ipcc_2019_2019}.

The Global Forest Carbon Database, ForC
(\url{https://forc-db.github.io/}), is the largest collection of
published estimates of forest C stocks, increments, and annual fluxes
\citep{anderson-teixeira_forc_2018, anderson-teixeira_carbon_2021}. ForC
includes data ingested from individual publications and relevant
databases, including the Global Reforestation Opportunity Assessment
(GROA) database \citep[database doi:
10.5281/zenodo.3983644]{cook-patton_mapping_2020}, and the global soil
respiration database
\citep[SRDB-V5,][]{bond-lamberty_global_2010, jian_restructured_2021}.
As of June 08, 2023, ForC contained 39848 records from 10589 plots in
1535 distinct geographical areas, along with records of stand age and
disturbance history. As such, ForC is positioned to improve
forest-related estimates of CO\textsubscript{2} emissions and removals
through the submission of data to the EFDB. The purpose of this
publication is to document that process and provide recommendations for
future improvements.

@@

Aboveground biomass, which is typically \textless200 t C
ha\textsuperscript{-1} but can exceed 700 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by the IPCC as ``all
biomass of living vegetation above the soil including stems, stumps,
branches, bark, seeds, and foliage''
\citep{ipcc_good_2003, ipcc_2006_2006}. IPCC's guidance is that the
understory may be excluded the understory if it constitutes a ``minor''
component \citep[defined as \textless{} 25 - 30 \% of emissions/removals
for the overall category,][]{ipcc_2006_2006}, and where a commonly
applied minimum size sampling threshold for mature forests would be 10
cm stem diameter at breast height (DBH). A recent study characterizing
the contributions of trees in different DBH classes to ecosystem C
stocks and fluxes found that trees 1 - 10 cm DBH contributed up to
\textasciitilde8\% aboveground biomass, \textasciitilde17\% aboveground
woody net primary productivity (\(ANPP_{woody.stem}\)), and
\textasciitilde20\% woody mortality (\(M_{woody}\)) of mature
closed-canopy forests worldwide \citep{piponiot_distribution_2022}, and
therefore stems \textless{} 10 cm DBH can generally be considered a
minor component of aboveground biomass for these forests. In regrowth
forests, woodlands, or savannas, small trees and shrubs contribute a
much larger proportion of C stocks and fluxes
\citep{lutz_global_2018, piponiot_distribution_2022, hughes_biomass_1999},
and, correspondingly, biomass estimates for these ecosystems tend
include smaller size classes. While IPCC guidance specifies that all
living vegetation should be included in biomass estimates, forest
censuses and biomass estimates do not consistently include life forms
other than dicot trees (e.g., lianas, ferns, palms, bamboo), although
these do tend to be censused when they constitute a large proportion of
the biomass \citep[e.g.,][]{fukushima_recovery_2007}. Further, it is
important to note that the IPCC definition of aboveground biomass
excludes standing dead wood, which is included in remote sensing biomass
estimates \citep{duncanson_aboveground_2021}.

@@

To create structure for EFDB-relevant records, we added a total of 15
new variables to the set of named and defined variables (Fig. 1),
counting each pair of variables with units in C (ending in \texttt{\_C})
or organic matter (ending in \texttt{\_OM}) as one. The majority of
these were increment variables (n=11), adding to only one previously
defined increment variable (aboveground biomass increment,
\emph{delta.agb}). These are directly related to C stocks as previously
defined in ForC, with ``\emph{delta.}'' added in front of the variable
name. Further, we added variables capturing the belowground component of
woody mortality (\emph{woody.mortality\_root}) and the combined
aboveground and belowground components of woody mortality
(\emph{woody.mortality}). Although most of these variables lacked
records in ForC as of June 08, 2023, their addition gave the structure
such that records can be populated over time. Finally, to provide better
definition of the previously existing variable \emph{organic.layer},
which has a nebulous definition that reflects the varied definitions
adopted by original studies, we added two clearly defined variables:
\emph{litter} (relatively undecomposed plant material/ OL horizon), and
\emph{O.horizon} (entire O-horizon, including OL).

@@

To submit complete, reviewed ForC records into EFDB, we created R
scripts to restructure ForC records and populate EFDB's bulk import form
(``EFDB bulk import.xlsx''). Criteria for data submission were that (1)
records had been checked against the original study and determined to be
complete and correct, and as originally presented, (2) the original
study presented values in tables or text, as opposed to the values
having been digitized from graphs or calculated based on related
variables, and (3) the records had not previously been submitted to
EFDB. Once converted into EFDB format, the records were reviewed and
then sent to the IPCC's Technical Support Unit for submission to EFDB.
Complete records needed to be reviewed by the EFDB editorial board and
then posted in the database -- a process that lags behind submission of
records and had not yet been completed for all records sent as of June
08, 2023.

@@

With input from the IPCC's Technical Support Unit, we reviewed the list
of ForC variables to identify those that were relevant to EFDB and to
appropriately map them into EFDB (Fig. 1). For each C pool (Table 1), we
identified variables representing organic matter or C stocks, stock
changes (a.k.a. ``net annual increments'' by IPCC, ``increments'' in
ForC), gains (a.k.a. ``gross annual increments'' by IPCC, ``fluxes'' in
ForC), and losses (``fluxes'' in ForC). As described in section 3.2, we
also defined 15 new EFDB-relevant variables that were not previously
represented in ForC. It is important to note that the correspondence of
ForC variables to IPCC criteria often depends upon measurement protocols
(``important sources of estimate variation'' in Table 1). For example,
ForC records of biomass and dead wood vary in the minimum stem diameter
censused, such that some records would match the IPCC criteria whereas
others would not. Information on minimum diameters censused and other
important sources of methodological variation are recorded as covariates
in ForC and mapped into the EFDB field \emph{Other Properties} (Appendix
B). Details on the mapping of ForC variables to EFDB -- including
associated covariates, IPCC pools (Table 1) and relevant equations
\citep{ipcc_2006_2006} -- are documented in the file
ForC\_variables\_mapping.csv in the GitHub repository associated with
this publication IPCC-EFDB-integration repository in ForC-db
organization (\url{https://github.com/forc-db/IPCC-EFDB-integration}).

@@

As of June 08, 2023, ForC (v4.0) contained 32693 independent records
(39848 total), 19316 of which were for the 42 variables relevant to EFDB
(Fig. 1). These records were distributed across all forested continents
and ecozones, albeit unevenly (Fig. 2). The largest number of records
came from Asia, followed by North America, South America, and Europe,
with relatively few records from Africa, Australia, and Oceania (Fig.
3c). Categorized by FAO ecozone, the greatest numbers of records came
from subtropical humid forests, temperate mountain systems, and tropical
rain forests, each with \textgreater2,000 independent records (Fig. 3b).
Boreal coniferous forests, temperate continental forests, subtropical
mountain systems, and tropical moist deciduous forests had
\textgreater1,000 independent records each, while other ecozones all had
\textless1,000 records. The most widely represented forest type was
needleleaf evergreen, followed by broadleaf deciduous and broadleaf
evergreen (Fig. 3a). In terms of stand age, the most represented age
class was 20-100 years, followed by \textless20 years and then
\textgreater100 years (Fig. 3d).

@@

As of June 08, 2023, we had reviewed or added 2292 EFDB-relevant
records, 1438 records of which were submitted to EFDB, and 376 of which
have been reviewed, accepted, and posted (Figs. 2-3, Table 2). The 37\%
attenuation between records reviewed and those sent to EFDB was
attributable to the presence of digitized records and records where a
variable's value had been calculated as the sum or difference of related
variables rather than presented directly in the text. The discrepancy
between the number of records sent and that posted to EFDB is primarily
attributable to the time required for the IPCC to review the records,
and it is not expected that many -- if any -- records will be rejected.

@@

The ForC database contains large numbers of records that could
potentially be useful for estimating C stock changes applying
methodological guidance provided by the IPCC. Here we have developed a
framework for submitting these records to the EFDB, thus making those
data more accessible for reporting CO\textsubscript{2} emissions and
removals from forest land consistent with good practice in the IPCC
guidelines \citep{ipcc_2006_2006, ipcc_2019_2019}. As of June 08, 2023,
we have submitted 1438 records to EFDB. Although this represents just
7\% of relevant records in ForC, it substantially increases the number
of forest land records in EFDB. The records submitted to EFDB and
present in ForC are very unevenly distributed across variables, regions,
and forest types (Figs. 2-3, Table 2), reflecting broader patterns in
allocation of research effort.

>>>>

\textbf{Abstract.} Forests are critical for climate change mitigation
and constitute a substantial portion of planned net emissions reductions
under the 2015 Paris Agreement. However, the efficacy of greenhouse gas
mitigation planning and reporting is dependent upon the quality of
available emission factors data, including forest carbon (C) stocks and
changes therein. Tens of thousands of relevant forest C estimates have
been published, yet are not readily accessible to the practitioners
compiling national greenhouse gas inventories. Many of these data have,
however, been compiled in the Global Forest C database (ForC;
https://forc-db.github.io/) and stand to be of value to greenhouse gas
inventories if made available through the Emission Factor Database
(EFDB) of the International Panel on Climate Change (IPCC). Here, we
develop and document a process for semi-automated submission of data
from ForC into the EFDB, assess the data available and submitted to
date, and provide recommendations for improving forest data collection,
analysis, and reporting to improve inventories of forest-sector
greenhouse gas emissions and removals. We begin by reconciling
terminology and mapping ForC fields into EFDB. This process required
some updates to the ForC database structure, leading to the release of a
new version of ForC (v4.0; described here). As of June 09, 2023, ForC
contained \textasciitilde19316 independent records relevant to EFDB,
1438 of which have been submitted to date. Among the data in ForC, there
is disproportionate representation of biomass (particularly aboveground)
stocks, with far fewer records for dead organic matter and soil C, and
relatively few or no records for net annual increments or C fluxes into
(gains) or out of (losses) the IPCC-defined C pools. Geographic
representation is also quite uneven, with the highest densities of
relevant records in temperate forests, and with relatively scant
representation of tropical forests in Africa and Asia. In the future,
forest C estimates in EFDB can be improved through targeted research to
fill critical gaps, reporting of information required by IPCC, and
continued submission of data from scientific publications to the EFDB.
Given that climate change is rapidly impacting the world's forests,
timely reporting of recent estimates will be especially critical to
accurate forest C inventories.

@@

To improve data accessibility for preparing greenhouse gas estimates,
the IPCC created the Emission Factor Database (EFDB;
\url{https://www.ipcc-nggip.iges.or.jp/EFDB/main.php}), which is
intended as a recognized library of emission factors and other
parameters that can be used for estimating greenhouse gas emissions and
removals. The EFDB can be used both for efforts to tally a nation's
intended or accomplished greenhouse gas reductions, or as a basis of
comparison for external parties to evaluate these inventories. The EFDB
encourages researchers to submit estimates of emission factors or other
related parameters from peer-reviewed journal papers or other accepted
sources for inclusion in the database. In the case of forests, emission
factors include C stocks, net annual increments, and annual fluxes for
various pools \citep{ipcc_2006_2006, ipcc_2019_2019}.

The Global Forest Carbon Database, ForC
(\url{https://forc-db.github.io/}), is the largest collection of
published estimates of forest C stocks, increments, and annual fluxes
\citep{anderson-teixeira_forc_2018, anderson-teixeira_carbon_2021}. ForC
includes data ingested from individual publications and relevant
databases, including the Global Reforestation Opportunity Assessment
(GROA) database \citep[database doi:
10.5281/zenodo.3983644]{cook-patton_mapping_2020}, and the global soil
respiration database
\citep[SRDB-V5,][]{bond-lamberty_global_2010, jian_restructured_2021}.
As of June 09, 2023, ForC contained 39848 records from 10589 plots in
1535 distinct geographical areas, along with records of stand age and
disturbance history. As such, ForC is positioned to improve
forest-related estimates of CO\textsubscript{2} emissions and removals
through the submission of data to the EFDB. The purpose of this
publication is to document that process and provide recommendations for
future improvements.

@@

Aboveground biomass, which is typically \textless200 t C
ha\textsuperscript{-1} but can exceed 700 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by the IPCC as ``all
biomass of living vegetation above the soil including stems, stumps,
branches, bark, seeds, and foliage''
\citep{ipcc_good_2003, ipcc_2006_2006}. IPCC's guidance is that the
understory may be excluded the understory if it constitutes a ``minor''
component \citep[defined as \textless{} 25 - 30 \% of emissions/removals
for the overall category,][]{ipcc_2006_2006}, and where a commonly
applied minimum size sampling threshold for mature forests would be 10
cm stem diameter at breast height (DBH). A recent study characterizing
the contributions of trees in different DBH classes to ecosystem C
stocks and fluxes found that trees 1 - 10 cm DBH contributed up to
\textasciitilde8\% aboveground biomass, \textasciitilde17\% aboveground
woody net primary productivity (\(ANPP_{woody.stem}\)), and
\textasciitilde20\% woody mortality (\(M_{woody}\)) of mature
closed-canopy forests worldwide \citep{piponiot_distribution_2022}, and
therefore stems \textless{} 10 cm DBH can usually be considered a minor
component of aboveground biomass for these forests. In regrowth forests,
woodlands, or savannas, small trees and shrubs contribute a much larger
proportion of C stocks and fluxes
\citep{lutz_global_2018, piponiot_distribution_2022, hughes_biomass_1999},
and, correspondingly, biomass estimates for these ecosystems tend
include smaller size classes. While IPCC guidance specifies that all
living vegetation should be included in biomass estimates, forest
censuses and biomass estimates do not consistently include life forms
other than dicot trees (e.g., lianas, ferns, palms, bamboo), although
these do tend to be censused when they constitute a large proportion of
the biomass \citep[e.g.,][]{fukushima_recovery_2007}. Further, it is
important to note that the IPCC definition of aboveground biomass
excludes standing dead wood, which is included in remote sensing biomass
estimates \citep{duncanson_aboveground_2021}.

@@

To create structure for EFDB-relevant records, we added a total of 15
new variables to the set of named and defined variables (Fig. 1),
counting each pair of variables with units in C (ending in \texttt{\_C})
or organic matter (ending in \texttt{\_OM}) as one. The majority of
these were increment variables (n=11), adding to only one previously
defined increment variable (aboveground biomass increment,
\emph{delta.agb}). These are directly related to C stocks as previously
defined in ForC, with ``\emph{delta.}'' added in front of the variable
name. Further, we added variables capturing the belowground component of
woody mortality (\emph{woody.mortality\_root}) and the combined
aboveground and belowground components of woody mortality
(\emph{woody.mortality}). Although most of these variables lacked
records in ForC as of June 09, 2023, their addition gave the structure
such that records can be populated over time. Finally, to provide better
definition of the previously existing variable \emph{organic.layer},
which has a nebulous definition that reflects the varied definitions
adopted by original studies, we added two clearly defined variables:
\emph{litter} (relatively undecomposed plant material/ OL horizon), and
\emph{O.horizon} (entire O-horizon, including OL).

@@

To submit complete, reviewed ForC records into EFDB, we created R
scripts to restructure ForC records and populate EFDB's bulk import form
(``EFDB bulk import.xlsx''). Criteria for data submission were that (1)
records had been checked against the original study and determined to be
complete and correct, and as originally presented, (2) the original
study presented values in tables or text, as opposed to the values
having been digitized from graphs or calculated based on related
variables, and (3) the records had not previously been submitted to
EFDB. Once converted into EFDB format, the records were reviewed and
then sent to the IPCC's Technical Support Unit for submission to EFDB.
Complete records needed to be reviewed by the EFDB editorial board and
then posted in the database -- a process that lags behind submission of
records and had not yet been completed for all records sent as of June
09, 2023.

@@

With input from the IPCC's Technical Support Unit, we reviewed the list
of ForC variables to identify those that were relevant to EFDB and to
appropriately map them into EFDB (Fig. 1). For each C pool (Table 1), we
identified variables representing organic matter or C stocks, net annual
increments, influxes (a.k.a. ``gross annual increments'' by IPCC), and
outfluxes. As described in section 3.2, we also defined 15 new
EFDB-relevant variables that were not previously represented in ForC. It
is important to note that the correspondence of ForC variables to IPCC
criteria often depends upon measurement protocols (``important sources
of estimate variation'' in Table 1). For example, ForC records of
biomass and dead wood vary in the minimum stem diameter censused, such
that some records would match the IPCC criteria whereas others would
not. Information on minimum diameters censused and other important
sources of methodological variation are recorded as covariates in ForC
and mapped into the EFDB field \emph{Other Properties} (Appendix B).
Details on the mapping of ForC variables to EFDB -- including associated
covariates, IPCC pools (Table 1) and relevant equations
\citep{ipcc_2006_2006} -- are documented in the file
ForC\_variables\_mapping.csv in the GitHub repository associated with
this publication IPCC-EFDB-integration repository in ForC-db
organization (\url{https://github.com/forc-db/IPCC-EFDB-integration}).

@@

As of June 09, 2023, ForC (v4.0) contained 32693 independent records
(39848 total), 19316 of which were for the 42 variables relevant to EFDB
(Fig. 1). These records were distributed across all forested continents
and ecozones, albeit unevenly (Fig. 2). The largest number of records
came from Asia, followed by North America, South America, and Europe,
with relatively few records from Africa, Australia, and Oceania (Fig.
3c). Categorized by FAO ecozone, the greatest numbers of records came
from subtropical humid forests, temperate mountain systems, and tropical
rain forests, each with \textgreater2,000 independent records (Fig. 3b).
Boreal coniferous forests, temperate continental forests, subtropical
mountain systems, and tropical moist deciduous forests had
\textgreater1,000 independent records each, while other ecozones all had
\textless1,000 records. The most widely represented forest type was
needleleaf evergreen, followed by broadleaf deciduous and broadleaf
evergreen (Fig. 3a). In terms of stand age, the most represented age
class was 20-100 years, followed by \textless20 years and then
\textgreater100 years (Fig. 3d).

@@

As of June 09, 2023, we had reviewed or added 2292 EFDB-relevant
records, 1438 records of which were submitted to EFDB, and 376 of which
have been reviewed, accepted, and posted (Figs. 2-3, Table 2). The 37\%
attenuation between records reviewed and those sent to EFDB was
attributable to the presence of digitized records and records where a
variable's value had been calculated as the sum or difference of related
variables rather than presented directly in the text. The discrepancy
between the number of records sent and that posted to EFDB is primarily
attributable to the time required for the IPCC to review the records,
and it is not expected that many -- if any -- records will be rejected.

@@

The ForC database contains large numbers of records that could
potentially be useful for estimating C stock changes applying
methodological guidance provided by the IPCC. Here we have developed a
framework for submitting these records to the EFDB, thus making those
data more accessible for reporting CO\textsubscript{2} emissions and
removals from forest land consistent with good practice in the IPCC
guidelines \citep{ipcc_2006_2006, ipcc_2019_2019}. As of June 09, 2023,
we have submitted 1438 records to EFDB. Although this represents just
7\% of relevant records in ForC, it substantially increases the number
of forest land records in EFDB. The records submitted to EFDB and
present in ForC are very unevenly distributed across variables, regions,
and forest types (Figs. 2-3, Table 2), reflecting broader patterns in
allocation of research effort.
